%%% master.tex
%%% Master Pandoc template 
%%% Created by Eric M. Fink (https://github.com/EricMFink/Pandoc/templates)
%%% Contents: 
%%% 1. Article: line 12
%%% 2. Syllabus: line 295
%%% 3. Vita: line 535
%%% 4. Legal Code: 683
%%% 6. Rules Handout: 842
%%% 7. Default: 999


% START OF SYLLABUS TEMPLATE

% ====================
% = Layout & Spacing =
% ====================

\documentclass[11pt,letterpaper,twoside]{article}
\usepackage[hmarginratio=1:1,top=1in,bottom=.75in,left=1.5in,right=1.5in]{geometry}
\usepackage{etoolbox}
\usepackage{marginnote}
\usepackage{sidenotes}
\usepackage{needspace}
\usepackage[defaultlines=3,all]{nowidow}
\raggedbottom
\usepackage{ragged2e}
\setlength{\RaggedRightParindent}{0em}
\RaggedRight
\usepackage[singlespacing]{setspace}
\usepackage[none]{hyphenat}
\usepackage{parskip}
\setlength{\parindent}{0em}
\setlength{\parskip}{0.6em plus 0.2em minus 0.1em}
\setlength{\emergencystretch}{3em}  % prevent overfull lines

% ==========================
% = Language & Date Format =
% ==========================

\usepackage[english]{babel}  
\usepackage{datetime}
\newdateformat{mydate}{\THEDAY-\monthname-\THEYEAR}
\usepackage{currfile}

% ==================
% = Colors & Fonts =
% ==================

\usepackage[table]{xcolor}
\definecolor{OffBlack}{HTML}{191919}
\definecolor{Maroon}{HTML}{800000}
\definecolor{TarHeelBlue}{HTML}{4b9cd3}
\definecolor{HopkinsBlue}{HTML}{002D72}
\definecolor{RacingGreen}{HTML}{004225}

\usepackage{fontspec}
\setmainfont{Athelas}[Mapping=tex-text]
\setsansfont{Adelle Sans}[Mapping=tex-text]
\setmonofont[Scale=0.90]{LFT Etica Mono}

\usepackage{textcomp}
\usepackage{amssymb}
\usepackage[]{ccicons}
\usepackage{fontawesome5}

% =======================
% = Headers and Footers = 
% =======================

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyfoot{}
\fancyfoot[C]{}
\fancyfoot[R]{\tiny\texttt{ Revised: \mydate\today}}
\fancyfoot[L]{}
\fancyhead[CE]{\textsc{Employment Law}}
\fancyhead[CO]{\textsc{Elon University School of Law}}
\fancyhead[LE]{\textsc{\thepage}}
\fancyhead[LO]{\textsc{Winter 2026}}
\fancyhead[RE]{\textsc{Prof. Fink}}
\fancyhead[RO]{\textsc{\thepage}}

% =========
% = Lists =
% =========

\usepackage{enumitem}
\setlistdepth{6}
\setlist[itemize]{leftmargin={1.5em}}
\providecommand{\tightlist}{%
\setlength{\itemsep}{0em}\setlength{\parskip}{0em}\setlength{\itemindent}{0em}}

% ============
% = Headings =
% ============

\usepackage[compact]{titlesec}
% \titlespacing*{<command>}{<left>}{<before-sep>}{<after-sep>}
\titlespacing*{\section}{0em}{0em}{.5em}
\titlespacing*{\subsection}{0em}{2em}{.5em}
\titlespacing*{\subsubsection}{0em}{1.5em}{.5em}
\titlespacing*{\paragraph}{0em}{1em}{0em}
\titlespacing*{\subparagraph}{0em}{.2em}{0em}

\setcounter{secnumdepth}{0}

% H1
\titleformat{\section}[block]
  {\huge\sffamily\color{Maroon}}
  {}
  {0em}
  {}

% H2
\titleformat{\subsection}[block]
  {\needspace{9\baselineskip}\LARGE\sffamily\color{Maroon}}
  {}
  {0em}
  {}
% H3
\titleformat{\subsubsection}[block]
  {\needspace{6\baselineskip}\Large\rmfamily\bfseries}
  {\thesubsection}
  {0em}
  {}
% H4
\titleformat{\paragraph}[block]
  {\footnotesize\sffamily\large\rmfamily\bfseries}
  {\thesubsubsection}
  {0em}
  {}
% H5
\titleformat{\subparagraph}[block]
  {\footnotesize\rmfamily}
  {}
  {0em}
  {}

% ==========
% = Quotes =
% ==========

\usepackage{csquotes}

\AtBeginEnvironment{quote}{\footnotesize\itshape} 

\renewenvironment{quote}{%
   \list{}{%
     \leftmargin2em   % this is the adjusting screw
     \rightmargin\leftmargin\parsep .1em }
   \item\relax
}
{\endlist}

% ==========
% = Tables =
% ==========

\usepackage{longtable,booktabs,array}
%\setlength\heavyrulewidth{0pt}
\usepackage{multirow}
\usepackage{calc}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\renewcommand{\arraystretch}{1.5}
\AtBeginEnvironment{longtable}{\footnotesize}

% =============
% = Footnotes = 
% =============

\usepackage[hang,flushmargin]{footmisc} 


% ==============
% = Hyperlinks =
% ==============

\usepackage[unicode=true]{hyperref}
\hypersetup{%
  colorlinks=true,
  allcolors=HopkinsBlue,
  breaklinks=true,
  pdfusetitle=true,
  pdfauthor={Eric M. Fink},
  pdftitle={Syllabus},
    pdfsubject={Employment Law},
      pdfproducer=LateX via pandoc,
  pdfcreator=LateX via pandoc
}

% ===============================
% ===== BEGIN DOCUMENT ==========
% ===============================

\begin{document}\thispagestyle{empty}

\color{OffBlack}

\section{Employment Law}

\begin{footnotesize}
\subparagraph{Elon University School of Law}
\subparagraph{Winter 2026}
\subparagraph{Room 107}
\subparagraph{Mondays \& Wednesdays, 10:30 am--12:15 pm}
\subparagraph{\url{emfink.net/EmploymentLaw}}
\vspace{1em}


\subparagraph{Eric M. Fink} 
\subparagraph{efink@elon.edu}
\subparagraph{336.279.9334} 
\subparagraph{Office Hours: {\url{calendly.com/emfink/}}}

\vspace{1em}

\end{footnotesize}

\vspace{1em}

\needspace{1\baselineskip}

\subsection*{Description}\label{description}
\addcontentsline{toc}{subsection}{Description}

This course surveys federal and state laws governing employment, in both
the individual and organized labor settings. Topics to be covered
include establishing an employment relationship; recruitment \& hiring;
the scope and limits of supervisory control; confidentiality \&
competition; wages \& hours; employee health \& safety; and termination
of employment.

After completing the course, you should be able to recognize and
diagnose legal issues arising in the employment context, analyze those
issues under the applicable law, and help clients avoid legal problems
or pursue remedies when they arise. Simulation problems, including
in-class discussion and take-home assignments, provide an opportunity to
develop practical skills for representing clients in employment matters.

\subsection*{Course Materials}\label{course-materials}
\addcontentsline{toc}{subsection}{Course Materials}

\subsubsection{Required}\label{required}

Employment Law: An Open-Source Casebook (version 4.1, December 2025).
Available on the course website:
\href{http://www.emfink.net/EmploymentLaw}{emfink.net/EmploymentLaw}.

Rachel Arnow-Richman \& Nantiya Ruan, Developing Professional Skills:
Workplace Law (West Academic 2017) (``Workbook'').

\subsubsection{Suggested}\label{suggested}

Richard A. Bales, Jeffrey M. Hirsch, \& Paul M. Secunda, Understanding
Employment Law (4th. ed.~Carolina Academic Press 2025)

\subsection*{Policies}\label{policies}
\addcontentsline{toc}{subsection}{Policies}

\subsubsection{Grading}\label{grading}

Your final grade for this course will be based on three take-home
problem assignments (25\% each) and participation in class discussions
(25\%). There will be no final exam.

The take-home problem assignments are due before class on the dates
indicated in the Schedule \& Assignments section of the syllabus. You
should submit each assignment to me by email \emph{no later than 10:00am
on the due date}. I will provide further information about these
assignments in class.

\subsubsection{Attendance}\label{attendance}

Elon Law School has adopted the following attendance policy for all
courses:

\begin{quote}
The Law School administers a policy that a student maintain regular and
punctual class attendance in all courses in which the student is
registered, including externships, clinical courses, or simulation
courses. Faculty members will give students written notice of their
attendance policies before or during the first week of class. These
policies may include, but are not limited to: treating late arrivals,
early departures, and/or lack of preparation as absences imposing grade
or point reductions for absences, including assigning a failing grade or
involuntarily withdrawing a student from the class and any other
policies that a professor deems appropriate to create a rigorous and
professional classroom environment.

In case of illness or emergency, students may contact the Office of
Student and Professional Life, which will then notify the student's
instructors. A student may notify the faculty member directly of a
planned absence and should refer to individual faculty members regarding
any policy that may apply. In the case of prolonged illness or
incapacity, the student should contact the
\href{https://www.elon.edu/u/law/students/}{Office of Student Life}.
\end{quote}

You should let me know (in advance if feasible) if you are unable to
attend class, will arrive late, or must leave early. I do not require an
explanation of the reason, nor do I require a doctor's note or other
documentation.

\subsubsection{Disability
Accommodations}\label{disability-accommodations}

For disability accommodation requests, contact the
\href{https://www.elon.edu/u/law/students/student-resources/academic-accommodations-accessibility/}{Office
of Academic Accommodations and Accessibility}.

\subsubsection{Honor Code}\label{honor-code}

The Law School
\href{https://www.elon.edu/u/law/students/honor-code/}{honor code}
applies to all activities related to your law school study, including
class meetings, assignments, and examinations.

\newpage

\subsection*{Schedule \& Assignments}\label{schedule-assignments}
\addcontentsline{toc}{subsection}{Schedule \& Assignments}

(\emph{Note:} This class will not meet on Monday, January 19th)

\subsubsection{1. Foundations of Employment
Law}\label{foundations-of-employment-law}

\paragraph{January 5 \& 7}\label{january-5-7}

\begin{itemize}
\tightlist
\item
  Employment as a Socio-Legal Relationship, \emph{Casebook} Chap. 1
\end{itemize}

\paragraph{January 12}\label{january-12}

\begin{itemize}
\tightlist
\item
  Labor Organizing \& Collective Bargaining, \emph{Casebook} Chap. 2
\end{itemize}

\subsubsection{2. Establishing an Employment
Relationship}\label{establishing-an-employment-relationship}

\paragraph{January 14}\label{january-14}

\begin{itemize}
\tightlist
\item
  Identifying Employees, \emph{Casebook} Chap. 3, § 1-3
\end{itemize}

\paragraph{January 21}\label{january-21}

\begin{itemize}
\tightlist
\item
  Identifying Employers, \emph{Casebook} Chap. 3, § 4
\end{itemize}

\paragraph{January 26}\label{january-26}

\begin{itemize}
\tightlist
\item
  Recruitment \& Hiring, \emph{Casebook} Chap. 4
\item
  Problem Assignment 1: Defamation (Workbook, Chap. 3)
\end{itemize}

\subsubsection{3.Scope \& Limits of Employer
Control}\label{scope-limits-of-employer-control}

\paragraph{January 28}\label{january-28}

\begin{itemize}
\tightlist
\item
  Privacy, Autonomy, \& Dignity, \emph{Casebook} Chap. 5, § 1
\end{itemize}

\paragraph{February 2}\label{february-2}

\begin{itemize}
\tightlist
\item
  Protected Concerted Activity, \emph{Casebook} Chap. 5, § 2
\end{itemize}

\paragraph{February 4}\label{february-4}

\begin{itemize}
\tightlist
\item
  Control Outside Work, \emph{Casebook} Chap. 5, § 3
\end{itemize}

\subsubsection{4. Employee Duties to
Employers}\label{employee-duties-to-employers}

\paragraph{February 9}\label{february-9}

\begin{itemize}
\tightlist
\item
  Confidentiality, \emph{Casebook} Chap. 6, § 1
\end{itemize}

\paragraph{February 11}\label{february-11}

\begin{itemize}
\tightlist
\item
  Loyalty, \emph{Casebook} Chap. 6, § 2
\end{itemize}

\paragraph{February 16}\label{february-16}

\begin{itemize}
\tightlist
\item
  Competition, \emph{Casebook} Chap. 6, § 2
\end{itemize}

\subsubsection{5. Wages \& Hours}\label{wages-hours}

\paragraph{February 18}\label{february-18}

\begin{itemize}
\tightlist
\item
  Minimum Wage, Overtime, \& Wage Payments, \emph{Casebook} Chap. 7
\item
  Problem Assignment 2: Wage \& Hour (Workbook, Chap. 11)
\end{itemize}

\subsubsection{6. Employee Health \&
Safety}\label{employee-health-safety}

\paragraph{February 23}\label{february-23}

\begin{itemize}
\tightlist
\item
  Medical Leave \& Disability Discrimination, \emph{Casebook} Chap. 8,
  §§ 1 \& 2
\end{itemize}

\paragraph{February 25}\label{february-25}

\begin{itemize}
\tightlist
\item
  OSHA \& Workers' Compensation, \emph{Casebook} Chap. 8, §§ 3 \& 4
\end{itemize}

\subsubsection{7. Terminating Employment}\label{terminating-employment}

\paragraph{March 2}\label{march-2}

\begin{itemize}
\tightlist
\item
  Express Contractual Provisions and Statutory Protections,
  \emph{Casebook} Chap. 9, § 1 \& 2
\end{itemize}

\paragraph{March 4}\label{march-4}

\begin{itemize}
\tightlist
\item
  Implied Contract and Tort Claims for Wrongful Termination,
  \emph{Casebook} Chap. 9, §§ 2 \& 3
\item
  Problem Assignment 3: Whistleblowers (Workbook, Chap. 4)
\end{itemize}

\paragraph{March 9}\label{march-9}

\begin{itemize}
\tightlist
\item
  Unemployment Compensation, \emph{Casebook} Chap. 9, § 4
\end{itemize}

\paragraph{March 11}\label{march-11}

\begin{itemize}
\tightlist
\item
  Make-up Class (if needed)
\end{itemize}

\end{document}

% END OF SYLLABUS TEMPLATE
